---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Calling C from R

I use `.Call` to call a function for computing danger in Jurassic Park

```{r danger}
library(IslaNublar)
Malcom() # Just a simple function in R

Park(people = 10, dino = 6)
```

## Working with class in C++

I test a simple Lotka-Volterra Model here. 
* lotka function use internal R with SEXP, but has a module in a different file (mod_prey).
* Costa function is defined in Rcpp, call a Rcpp constructor and some the prey void function is still defined with SEXP

```{r}
library(IslaNublar)
n = 50
K = 50
res <- lotka(prey_t = 10, pred_t = 10, prey_gr = 0.26, pred_gr = -0.32,
             prey_K = K, pred_K = K, 
             int_predprey = -0.04, int_preypred = 0.019, n = n, verbose = FALSE)

rest <- Costa(10, 0.26, K, -0.04,
              10, -0.32, K, 0.019, n, verbose = FALSE)

plot(1, type = "n", xlim = c(0, n), ylim = c(0, K+ 0.1*K))
lines(res[[1]], col = "darkgreen")
lines(res[[2]], col = "darkred")
lines(rest[[1]], col = "green", type = "p",pch = 3)
lines(rest[[2]], col = "red", type = "p", pch = 3)
```
## Using SEXP pointeurs

```{r}
library(IslaNublar)
n = 15
K = 50
res <- Costa(10, 0.26, K, -0.04,
              10, -0.32, K, 0.019, n, verbose = FALSE)

rest <- Sorna(list(10, 0.26, K, -0.04),
              list(10, -0.32, K, 0.019), n, verbose = TRUE)

plot(1, type = "n", xlim = c(0, n), ylim = c(0, K+ 0.1*K))
lines(res[[1]], col = "darkgreen")
lines(res[[2]], col = "darkred")
lines(rest[[1]], col = "green", type = "p",pch = 3)
lines(rest[[2]], col = "red", type = "p", pch = 3)
```

